---
title:  'Coding Challenge #4'
subtitle: 'SWORK 881'
author:
- name: Student -  [Your name goes here]
output: html_document
---

## load libraries
```{r}

```

## load dataset
```{r}



```


#data wrangling

We will be creating new variables: 
`anxiety` = clincally significant symptoms of anxiety; score 3 or more on PHQ-4 items 1 & 2
`depression` = clinically significant symptoms of depression; score of 3 or mroe on PHQ-4 items 3 & 4 
`distress` = continuous PHQ-4 score; higher score indicate greater distress
`distress_type` = multinomial variable: 0- none; 1- anxiety; 2- dep; 3- anxiety & dep
(hint: use `str_c(var1, '', var2)` to concatenate two values by rows)
`distress_cat` = categorizing distress score into min:4 ~ 'low'; 5:8 ~ 'mid'; 8:max ~ 'high'
(hint: use `%in%`)
`age_sd` = standardized `age` variable


```{r}


```

Report frequency of `distress_type`
> [ Answer goes here  ].

_hint_: your **none** category must have $n=322$; if you do not have this, check your code again.


Report frequency of `distress_cat`
> [ Answer goes here ].

_hint_: your **mid** category must have $n=170$; if you do not have this, check your code again.

---
## multinomial logistic regression

Run multinomial regression where DV is `distress_type`. Use `anxiety` as your reference category. 
Use your typical list of independent variables (standardized age, sex, education). 
 
_hint_: use `nnet` package's `multinom` function

```{r}

```

Please note your interpretation unit and your outcome unit must be the same. If needed, trasnform your output to facilitate  your interpretation.

Focusing on those who reported both _anxiety_ **AND** _depression_ as your outcome level of interest, provide your interpretation below:
> [Provide your interpretation here]


---
## ordinal logistic regression

Run ordinal regression where DV is `distress_cat`. Use your typical list of independent variables (standardized age, sex, education).

```{r}


```
To the best of your knowledge, provide explanation of the result. 

> [Provide your description of the result here]


---
## splines!

Run linear regression where DV is `distress`. For your standardized age variable, locate knot points at `-0.5`, `0`, and `0.5`. 

```{r}

```

Provide your interpretation below:
> [Provide your interpretation here]


Run logistic regression where DV is `depression`. For your standardized age variable, locate knot points at  `-1`, `0`, and `1`. 

```{r}

```
Provide your interpretation below:
> [Provide your interpretation here]
